A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-18 paper.tex
conflict

@@

\begin{proof}
We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$, integrating out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  We can then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}.  At $t=0$, we are left with the holomorphic twist from Theorem \ref{2d_minimal_twist_thm}, i.e, the theory $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  The action functional is further deformed by the remaining $t$-linear terms, which together take the form
\[\int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right).\]
In terms of the classical BV complex we can identify these terms as introducing the following dotted isomorphism between two summands:
\[\xymatrix@R=0.4cm@C=0.2cm{
\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
}\]
This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
\end{proof}

@@

Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.  Indeed, let $W_3$ be the 2d auxiliary space in the 3d $\mc N=2$ supertranslation algebra.  The 3d spin representation $S \otimes W_3$ splits into $S_+ \otimes W_3 \oplus S_- \otimes W_3$ as a $\spin(2;\CC)$-module.  Rank one square zero elements in 3d $\mc N=2$ generically become rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.  There is a square-zero supercharge in 3d $\mc N=2$ compatible with the identity twisting homomorphism $\spin(2;\CC) \to \spin(2;\CC)$.  This becomes the B-twisting homomorphism of $\spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ of weight $(1,-1)$ in the 2d $\mc N=(2,2)$-algebra.

>>>>

First, we record the minimal twist of 2d $\cN=(2,2)$ supersymmetric Yang--Mills theory.

@@

\begin{proof}
We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
The resulting action functional is of the form
\[
S_{BF} + \int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right)\]
Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.

We can identify the linearized BV complex with the following diagram:
\[\xymatrix@R=0.4cm@C=0.2cm{
\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
}\]
Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
\end{proof}

@@

Finally, there is the $B$-twist of 2d $\cN=(2,2)$ supersymmetry.
This twist arises from the twist of 3d $\cN=2$ via dimensional reduction in a non-invariant direction.  
Indeed, let $W_3$ be the two-dimensional auxiliary space in the 3d $\mc N=2$ supertranslation algebra.  
As a $\spin(2;\CC)$-representation, the 3d $\cN=2$ spinorial representation decomposes as $S_+ \otimes W_3 \oplus S_- \otimes W_3$.
Generically, rank one square zero elements in 3d $\mc N=2$ supersymmetry define rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.  
There is a square-zero supercharge in 3d $\mc N=2$ compatible with the identity twisting homomorphism $\spin(2;\CC) \to \spin(2;\CC)$.  This becomes the B-twisting homomorphism of $\spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ of weight $(1,-1)$ in the 2d $\mc N=(2,2)$-algebra.
